---
title: "VALLURU_M_4"
output: html_notebook
---

Install packages
```{r}
install.packages("openxlsx", dependencies = TRUE)

library(openxlsx)    # used to open the .xlsx file
library(lubridate)   # used to clean up the dates
library(stringr)     # used to rewrite strings
```



Set the working directory
```{r}
setwd("D:/Mahitha/DataScience/HW4")
```





Function that loads the data frame
```{r}

loadDF <- function() {
  if(!exists("farmersmarkets")) {
    farmersmarkets <- read.xlsx("2013FarmersMarkets.xlsx", startRow=3)
  }
}

```


Load the data frame
```{r}
loadDF()
```

We will have to delete the records that have NA as in its Season1Date column.
```{r}
cleanDatesDF <- farmersmarkets[which(!is.na(farmersmarkets["Season1Date"])),]
farmersmarkets <- cleanDatesDF
```

We will have to make rules about the seasons:
WINTER = December, January, February
SPRING = March, April, May
SUMMER = June, July, August
FALL   = Septemebr, October, November
Half-year = Between 180 and 300 days
Full-year = 300+ days
```{r}
threeColumns <- as.data.frame(str_split_fixed(farmersmarkets$Season1Date, " ", n=3)) # split into 3 columns

```

So if we have "MM/DD/YY to MM/DD/YY", we will split it into 3 columns that separate it into "MM/DD/YY", "to", and "MM/DD/YY"
```{r}
colnames(threeColumns) <- c("first_date", "grammar", "second_date")
threeColumns$first_date <- as.character(threeColumns$first_date) # standardize all dates as characters for now
threeColumns$second_date <- as.character(threeColumns$second_date) # standardize all dates as characters for now
```

Remove the values with NA as the second_date value
```{r}
cleanSecondDatesDF <- threeColumns[which(!is.na(threeColumns["second_date"])),]
farmersmarkets <- cleanSecondDatesDF
```



Now, we have to create a function that helps us classify which dates go with the month.
```{r}
scale <- data.frame(month = c("January","February","March",
                               "April","May","June",
                              "July","August","September",
                              "October","November","December"),

                     date = c("01/01/2012", "02/01/2012",
                                      "03/01/2012", "04/01/2012",
                                      "05/01/2012", "06/01/2012",
                                      "07/01/2012", "08/01/2012",
                                      "09/01/2012", "10/01/2012",
                                      "11/01/2012", "12/01/2012"))
```


Classify as the date
```{r}
scale$date <- as.Date(helper$date, format = "%m/%d/%Y")
```


Convert all the dates so that they are in the same format
```{r}
dateConversion <- function(x){
if(!str_detect(x, '/') == TRUE){ # if the observation doesn't contain '/'...
  data <- as.Date(scale$date[match(x,scale$month)]) #...use the scale helper table and classify it as a date
} 
  else{
    data <- as.Date(x, format = "%m/%d/%Y") # otherwise turn it into a date object
  }
  return(as.Date(data))
}
```




Using the farmersmarkets data frame, insert the new date
```{r}

farmersmarkets$first_date <- as.Date(sapply(threeColumns$first_date, dateConversion),origin = "1970-01-01") 
farmersmarkets$second_date <- as.Date(sapply(threeColumns$second_date, dateConversion),origin = "1970-01-01") 
farmersmarkets$time_diff <- farmersmarkets$second_date - farmersmarkets$first_date 
farmersmarkets$half_way <- farmersmarkets$time_diff/2 + farmersmarkets$first_date 



```


Function to determine date
```{r}
getSeason <- function(DATES) {
  WI <- as.Date("2012-12-01", format = "%Y-%m-%d") # WINTER
  SP <- as.Date("2012-3-01",  format = "%Y-%m-%d") # SPRING
  SU <- as.Date("2012-6-01",  format = "%Y-%m-%d") # SUMMER
  FA <- as.Date("2012-9-01",  format = "%Y-%m-%d") # FALL
  
  # Convert dates from any year to 2012 dates
  d <- as.Date(strftime(DATES, format="2012-%m-%d"))
  
  ifelse (d >= WI | d <  SP, "Winter", 
          ifelse (d >=  SP & d < SU, "Spring",
                  ifelse (d >= SU & d < FA, "Summer", "Fall")))
}

```


For loop to apply the function to each date
```{r}
for(i in 1:nrow(farmersmarkets)){ # for each row in the farmersmarkets data frame
  if(is.na(farmersmarkets$time_diff[i])){ # if the record is NA give the period NA
    farmersmarkets$period[i] <- NA 
  } 
  else {
    if(farmersmarkets$time_diff[i] <= 180){  # if time period is less than 180 days
      farmersmarkets$period[i] <- getSeason(farmersmarkets$half_way[i]) # we should consider it a season: Winter, Spring, Summer or Fall based on the date at the half way point of the time interval
    } 
    else if ((farmersmarkets$time_diff[i] <= 300) ==TRUE){ # if it's greater than 180, but less than 300
      farmersmarkets$period[i] <- "Half-Year" # we'll consider it a "Half-Year" 
    } 
    else {
      farmersmarkets$period[i] <- "Full-Year" # for anything else greater than 300 days, we'll consider it a full year, the reasoning being it wouldn't be appropriate to call, for example, a 10-month long farmer's market a "half year" one. 
    }
  }
  i <- i + 1 # keep the for loop going
}
```



Add farmersmarkets$period that contains all of the season categories:
```{r}
farmersmarkets$period <- as.factor(farmersmarkets$period)

print(farmersmarkets$period)


```



Create a function that determines which markets accept WIC
```{r}

# Function: acceptsWIC
# Finds all the markets which accept WIC
# Args: None
# Returns: a dataframe containing all of the markets which accept WIC
acceptsWIC <- function() {
  result <- farmers_markets[which(farmers_markets["WIC"] == "Y"),]
  return(result)
}
```







