---
title: "VALLURU_M_6"
output: html_notebook
---



Load any necessary libraries.



```{r}



library(XML)

```


Function that helps to load the dataframe.
```{r}



loadBiddingDF <- function() {
  if (!exists("bidding")) {
    biddingParse <- xmlTreeParse("http://aiweb.cs.washington.edu/research/projects/xmltk/xmldata/data/auctions/ebay.xml", useInternalNodes = TRUE)
    biddingRoot <- xmlRoot(biddingParse)
  }
}
```



```{r}
loadBiddingDF()
```



Now that we have done this, we can now see more information about the data.
When typing in
```{r}
xmlName(biddingRoot)
```
We get the result: [1] "root"



Now to see how many child nodes there are, we can use
```{r}
names(biddingRoot)
```
And that gives us: [1] "listing" "listing" "listing" "listing" "listing"
So there are 5 listings in this set.



Now we can look more into what categories there are by using
```{r}
names(biddingRoot[[1]])
```
And we get:
 seller_info           payment_types           shipping_info   buyer_protection_info            auction_info 
"seller_info"         "payment_types"         "shipping_info" "buyer_protection_info"          "auction_info" 

 bid_history               item_info 
"bid_history"             "item_info" 





We know that the number of bids is under the "Auction info" section, so we should go through each listing and create a dataframe with all of the listings' names and the number if highest bids they have.
```{r}
# Create a dataframe with empty values for now, but they will be filled soon
Name = c(NA, NA, NA, NA, NA)            # for the name of the auction
NumberBids = c(NA, NA, NA, NA, NA)      # for keeping track of how many bids occurred in each auction
bidsDF = data.frame(Name, NumberBids)   # creates teh data frame with the two columns
```



To get names, we need to get the xml Value of each listing.
This function will update the names of the auctions for all 5 listings.
Args: None
Returns: None
```{r}
loadNames <- function() {
  # a for loop to go through each row in the Name column
  for(i in 1:nrow(bidsDF)) {
    # grabs the specific name of the auction from the XML tree
    bidsDF[i,1] <- xmlValue(biddingRoot[[i]][[1]][[1]])
  }
}

```






To get the number of bids, we need to get the xml value of each listing.
This function will update all the numbers of bids the respective auction received for all 5 listings.
Args: None
Returns: None
```{r}
loadBidNumbers <- function() {
  # a for loop to go through each row in the NumberBids column
  for(i in 1:nrow(bidsDF)) {
    # grabs the specific number from the XML tree
    bidsDF[i,2] <- as.numeric(xmlValue(biddingRoot[[i]][[5]][[5]]))
  }
}

```






Determines the number of auctions that had more than 5 bids.
Args: None
Returns: A number that represents the number of auctions with more than 5 bids.
```{r}
moreFiveBids <- function() {
  # a counter to keep track of the number of auctions with more than 5 bids
  track = 0 
  # a for loop that goes through each row in the bidsDF dataframe
  for(i in 1:nrow(bidsDF)) {
    # if statement to decide if the number of bids for a particular auction is more than 5
    if(as.numeric(bidsDF[i,2]) > 5) { 
      track = track + 1 # if so, add 1 to the counter
    }
  }
  # return the counter
  return(track)
}
```



```{r}
moreFiveBids()
```


SECOND QUESTION


```{r}
install.packages("RCurl")
install.packages("bitops")
install.packages("xml2")
library(bitops)
library(RCurl)
library(XML)
library(xml2)
```



Trade
```{r}
loadTradeDF <- function() {
  fileURL <- "file://D:/Mahitha/DataScience/HW6/getHistory15.xml"
  xData <- getURL(fileURL)
  doc <- xmlTreeParse(xData)
  tradeRoot <- xmlRoot(doc)
}
```



```{r}
xmlName(tradeRoot)
```



```{r}
names(doc[[1]][[1]])

```



As you can see, the very first one does not count, as it is just information and has nothing to do with the actual data.
```{r}
names(doc[[1]][[1]][[1]])
```


This is a more appropriate look into what categories there are.
```{r}
names(doc[[1]][[1]][[2]])
```



Create a data frame
```{r}
Symbol = c(NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
           NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
           NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
           NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
           NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
           NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
           NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
           NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
           NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
           NA,NA,NA)
TimeStart = c(NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
              NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
              NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
              NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
              NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
              NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
              NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
              NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
              NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
              NA,NA,NA)
TimeEnd = c(NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
            NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
            NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
            NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
            NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
            NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
            NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
            NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
            NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
            NA,NA,NA)
Price = c(NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
          NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
          NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
          NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
          NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
          NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
          NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
          NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
          NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
          NA,NA,NA)
Volume = c(NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
           NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
           NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
           NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
           NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
           NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
           NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
           NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
           NA,NA,NA,NA,NA,NA,NA,NA,NA,NA,
           NA,NA,NA)

tradesDF <- data.frame(Symbol, TimeStart, TimeEnd, Price, Volume)
```




Fill in the dataframe for Symbol
```{r}

loadSymbol <- function() {
  for(i in 2:nrow(tradesDF)) {
    tradesDF[i,1] <- xmlValue(doc[[1]][[1]][[i]][[1]])
  }
}



```



Fill in the dataframe for TimeStart
```{r}

loadTimeStart <- function() {
  for(i in 2:nrow(tradesDF)) {
    tradesDF[i,2] <- substr(xmlValue(doc[[1]][[1]][[i]][[2]]), 12, 19)
  }
}



```



FIll in the dataframe for TimeEnd
```{r}


loadTimeEnd <- function() {
  for(i in 2:nrow(tradesDF)) {
    tradesDF[i,3] <- substr(xmlValue(doc[[1]][[1]][[i]][[2]]), 21, 27)
  }
}
```


Fill in the dataframe for the highest closing Price
```{r}


loadPrice <- function() {
  for(i in 2:nrow(tradesDF)) {
    tradesDF[i,4] <- as.numeric(xmlValue(doc[[1]][[1]][[i]][[7]]))
  }
}
```




Fill in the dataframe for the Volume
```{r}

loadVOlume <- function() {
  for(i in 2:nrow(tradesDF)) {
    tradesDF[i,5] <- as.numeric(xmlValue(doc[[1]][[1]][[i]][[8]]))
  }
}
```



Because the first row is negligible, we will create a new dataframe without the first row.
```{r}
tradesDF <- tradesDF[-1,]
```






Calculates the maximum closing price for the security.
Args: None
Returns: None
```{r}
highestClosingPrice <- function() {
  return(apply(tradesDF,4, max, trim = 0))
}
```





Calculates the total volume that was traded for the day.
Args: None
Returns: A number indicating the volume that was traded.
```{r}
totalVolume <- function() {
  counter <- 0
  
  for(i in 1:92) {
    counter = counter + tradesDF[i,5]
  }
  
  return(counter)
}
```





Analyzes the average trading volume for that particular day by the hour.
Args: None.
Returns: A dataframe that consists of the hour and the average trading colume for that hour.
```{r}
averageVolume <- function() {
  zero <- c(NA, NA)
  one <- c(NA, NA)
  two <- c(NA, NA)
  three <- c(NA, NA)
  four <- c(NA, NA)
  five <- c(NA, NA)
  six <- c(NA, NA)
  seven <- c(NA, NA)
  eight <- c(NA, NA)
  nine <- c(NA, NA)
  ten <- c(NA, NA)
  eleven <- c(NA, NA)
  twelve <- c(NA, NA)
  thirteen <- c(NA, NA)
  fourteen <- c(NA, NA)
  fifteen <- c(NA, NA)
  sixteen <- c(NA, NA)
  seventeen <- c(NA, NA)
  eighteen <- c(NA, NA)
  nineteen <- c(NA, NA)
  twenty <- c(NA, NA)
  twentyone <- c(NA, NA)
  twentytwo <- c(NA, NA)
  twentythree <- c(NA, NA)
  twentyfour <- c(NA, NA)
  
  DF <- data.frame(one, two, three, four, five, six, seven, eight, nine, ten, eleven, twelve, thirteen, fourteen, fiften, sixteen, seventeen, eighteen, nineteen, twenty, twentyone, twentytwo, twentythree, twentyfour)
  
}
```






