---
title: "R Notebook"
output: html_notebook
---

Install and Load the appropriate libraries.

```{r}
install.packages("RCurl")
install.packages("scrapeR")
library(RCurl)
library(XML)
library(scrapeR)
```


Get the URL and its path
```{r}
powerball <- getURL("http://www.powerball.com/powerball/pb_nbr_history.asp?startDate=11%2F11%2F2015&endDate=2%2F15%2F2017")

powerball <- readLines(tc <- textConnection(powerball))

```


```{r}
powerballPagetree <- htmlTreeParse(powerball, useInternalNodes = TRUE)
```



Create a dataframe.
```{r}
DrawDate = unlist(xpathApply(powerballPagetree, "//*/tr[@valign='middle']/td[1]", xmlValue))
WhiteBall1 = unlist(xpathApply(powerballPagetree, "//*/tr[@valign='middle']/td[2]", xmlValue))
WhiteBall2 = unlist(xpathApply(powerballPagetree, "//*/tr[@valign='middle']/td[3]", xmlValue))
WhiteBall3 = unlist(xpathApply(powerballPagetree, "//*/tr[@valign='middle']/td[4]", xmlValue))
WhiteBall4 = unlist(xpathApply(powerballPagetree, "//*/tr[@valign='middle']/td[5]", xmlValue))
WhiteBall5 = unlist(xpathApply(powerballPagetree, "//*/tr[@valign='middle']/td[6]", xmlValue))
PowerBall = unlist(xpathApply(powerballPagetree, "//*/tr[@valign='middle']/td[8]", xmlValue))

loadDF <- data.frame(DrawDate, WhiteBall1, WhiteBall2, WhiteBall3, WhiteBall4, WhiteBall5, PowerBall)
```




Create an empty dataframe.
```{r}

Ball1 = c(1:69)
Ball2 = c(1:69)
Ball3 = c(1:69)
Ball4 = c(1:69)
Ball5 = c(1:69)
PowerballRange = c(1:69)
OccurenceDF <- data.frame(Ball1, Ball2, Ball3, Ball4, Ball5, PowerballRange)

```


Go through the original DF and go through each number.
```{r}
for(i in 1:nrow(OccurenceDF)) {
  Ball1[i] <- 0
  OccurenceDF <- data.frame(Ball1, Ball2, Ball3, Ball4, Ball5, PowerballRange)
}

for(i in 1:nrow(loadDF)) {
  x <- as.numeric(WhiteBall1[i])
  Ball1[x] <- Ball1[x] + 1
  
  OccurenceDF <- data.frame(Ball1, Ball2, Ball3, Ball4, Ball5, PowerballRange)
}
```



Go through the original DF and go through each number.
```{r}
for(i in 1:nrow(OccurenceDF)) {
  Ball2[i] <- 0
  OccurenceDF <- data.frame(Ball1, Ball2, Ball3, Ball4, Ball5, PowerballRange)
}

for(i in 1:nrow(loadDF)) {
  x <- as.numeric(WhiteBall2[i])
  Ball2[x] <- Ball2[x] + 1
  
  OccurenceDF <- data.frame(Ball1, Ball2, Ball3, Ball4, Ball5, PowerballRange)
}
```




Go through the original DF and go through each number.
```{r}
for(i in 1:nrow(OccurenceDF)) {
  Ball3[i] <- 0
  OccurenceDF <- data.frame(Ball1, Ball2, Ball3, Ball4, Ball5, PowerballRange)
}

for(i in 1:nrow(loadDF)) {
  x <- as.numeric(WhiteBall3[i])
  Ball3[x] <- Ball3[x] + 1
  
  OccurenceDF <- data.frame(Ball1, Ball2, Ball3, Ball4, Ball5, PowerballRange)
}
```


Go through the original DF and go through each number.
```{r}
for(i in 1:nrow(OccurenceDF)) {
  Ball4[i] <- 0
  OccurenceDF <- data.frame(Ball1, Ball2, Ball3, Ball4, Ball5, PowerballRange)
}

for(i in 1:nrow(loadDF)) {
  x <- as.numeric(WhiteBall4[i])
  Ball4[x] <- Ball4[x] + 1
  
  OccurenceDF <- data.frame(Ball1, Ball2, Ball3, Ball4, Ball5, PowerballRange)
}
```



Go through the original DF and go through each number.
```{r}
for(i in 1:nrow(OccurenceDF)) {
  Ball5[i] <- 0
  OccurenceDF <- data.frame(Ball1, Ball2, Ball3, Ball4, Ball5, PowerballRange)
}

for(i in 1:nrow(loadDF)) {
  x <- as.numeric(WhiteBall5[i])
  Ball5[x] <- Ball5[x] + 1
  
  OccurenceDF <- data.frame(Ball1, Ball2, Ball3, Ball4, Ball5, PowerballRange)
}
```




Go through the original DF and go through each number.
```{r}
for(i in 1:nrow(OccurenceDF)) {
  PowerballRange[i] <- 0
  OccurenceDF <- data.frame(Ball1, Ball2, Ball3, Ball4, Ball5, PowerballRange)
}

for(i in 1:nrow(loadDF)) {
  x <- as.numeric(PowerBall[i])
  PowerballRange[x] <- PowerballRange[x] + 1
  
  OccurenceDF <- data.frame(Ball1, Ball2, Ball3, Ball4, Ball5, PowerballRange)
}
```


Ball Number from Ball1 that occurred most frequently
```{r}
which.max(OccurenceDF$Ball1)
```



Ball Number from Ball2 that occurred most frequently
```{r}
which.max(OccurenceDF$Ball2)
```



Ball Number from Ball3 that occurred most frequently
```{r}
which.max(OccurenceDF$Ball3)
```



Ball Number from Ball4 that occurred most frequently
```{r}
which.max(OccurenceDF$Ball4)
```



Ball Number from Ball5 that occurred most frequently
```{r}
which.max(OccurenceDF$Ball5)
```





Number from Powerball that occurred most frequently
```{r}
which.max(OccurenceDF$PowerballRange)
```



Which ball number occurred highest of all 6 balls

```{r}
one <- max(OccurenceDF$Ball1)
two <- max(OccurenceDF$Ball2)
three <- max(OccurenceDF$Ball3)
four <- max(OccurenceDF$Ball4)
five <- max(OccurenceDF$Ball5)
power <- max(OccurenceDF$PowerballRange)

numbers <- data.frame(one, two, three, four, five, power)

max <- 0
if (one > max) { 
  max <- one
}
if (two > max) {
  max <- two
}
if (three > max) {
  max <- three
}
if (four > max) {
  max <- four
}
if (five > max) {
  max <- five
}
if (power > max) {
  max <- power
}


outputHighest <- function() {
  if (max == one) {
    return(which.max(OccurenceDF$Ball1))
  }
  if (max == two) {
  return(which.max(OccurenceDF$Ball2))
  }
  if (max == three) {
  return(which.max(OccurenceDF$Ball3))
  }
  if (max == four) {
  return(which.max(OccurenceDF$Ball4))
  }
  if (max == five) {
  return(which.max(OccurenceDF$Ball5))
  }
  if (max == power) {
  return(which.max(OccurenceDF$PowerballRange))
  }
}

```


```{r}
outputHighest()
```




Here are the individual occurrences for which balls occurred how many times
```{r}
factor(OccurenceDF$Ball1, levels = c(1:69))
```


```{r}
factor(OccurenceDF$Ball2, levels = c(1:69))
```


```{r}
factor(OccurenceDF$Ball3, levels = c(1:69))
```


```{r}
factor(OccurenceDF$Ball4, levels = c(1:69))
```


```{r}
factor(OccurenceDF$Ball5, levels = c(1:69))
```


```{r}
factor(OccurenceDF$PowerballRange, levels = c(1:69))
```



As you can see, the amount of Balls for Ball1 is usually in the early numbers. They are rarely in the last numbers, from 35 to 69.
The distribution of the balls later on have increased as the Ball number increases.
This does not include the Powerball, as it can clearly be seen that it follows the trend of Ball1.










