---
title: "VALLURU_M_3"
output: html_notebook
---


Let's load the libraries needed.
```{r}
require(lubridate)  # great package for manipulating dates
```


First, I'd like to set a working directory to the place where I have the csv file.
```{r}
# set working directory
setwd("D:/Mahitha/DataScience/HW3")
```

Now, I have to load the csv file into a dataframe. I'll do this by creating a function.
Also, I think it's best to clean up the FlightDate and FlightYear fields, which I'll do using lubridate.
```{r}
loadDF <- function() {
  if (!exists("birdstrikes")) {
    birdstrikes <- read.csv("Bird\ Strikes.csv")
    
    # cleans up FlightDate column
    birdstrikes$FlightDate <- as.Date(birdstrikes$FlightDate, format = "%d/%m/%Y")
    # creates a new column called FlightYear, just shows the year of incident
    birdstrikes$FlightYear <- year(as.Date(birdstrikes$FlightDate, format = "%d/%m/%Y"))
  }
}
```

Loads the data.
```{r}
loadDF()
```

Function that returns which year had the most bird strikes
```{r}
# Gets the year of the greatest number of strikes 
# Args: none
# Returns: an number representing the year
mostStrikesInaYear <- function() {
  # create a table using birdstrikes but only showing the FlightYear column
  tableYear = table(birdstrikes$FlightYear)
  
  # sort this table in DECREASING order (most strikes in a year first)
  sortedTableYear = sort(tableYear, decreasing = TRUE)
  
  # get the name of the FIRST element in this sorted table, which is the year with the most bird strikes
  getName = names(sortedTableYear[1])
  
  #return getName
  return(getName)
}

# Return value: 2010
```

Function that returns a dataframe containing the year and number of bird strikes
```{r}
# Creates a datafram with the year and number of brid strikes
# Args: none
# Returns: A dataframe
strikesByYear <- function() {
  #create a table using birdstrikes but only showing the FlightYear column
  tableYear = table(birdstrikes$FlightYear)
  
  # create dataframe
  yearDF = as.data.frame(tableYear)
  
  return(yearDF)
}
```

Function that returns the number of bird strike incidents per airline (not military or business) and stores the result in a dataframe.
```{r}
# Returns a dataframe that calculates the number of bird strikes per airline, not including military or business
# Args: none
# Returns: a dataframe
strikesByAirline <- function() {
  # create a table using birdstrikes but only showing the Airline Operator column
  tableAirlineOperator = as.data.frame(table(birdstrikes$Aircraft..Airline.Operator))
  
  names(tableAirlineOperator)[1] = "Airline Operator"
  
  # now exclude the business and military operators from tableAirlineOperator
  tableAirlineOperator = tableAirlineOperator[which(tableAirlineOperator["Airline Operator"] != "MILITARY" &
                                                           tableAirlineOperator["Airline Operator"] != "BUSINESS"),]
  
  # create a dataframe
  AirlineStrikes = as.data.frame(tableAirlineOperator)
  
  return(AirlineStrikes)
}
```

Function that returns the airline with the most amount of bird strikes. Disregards UNKNOWN.
```{r}
# Returns the airline with the most bird strikes
# Args: AirlineStrikes (a dataframe with the airline and the number of bird strikes for each)
# Returns: an airline (a string)
mostStrikes <- function(AirlineStrikes) {
  removeUnknown <- AirlineStrikes[which(AirlineStrikes["Airline Operator"] != "UNKNOWN"),]

  result <- removeUnknown[which(removeUnknown["Freq"] == max(removeUnknown["Freq"])),1]

  return(result)
}

# Return Value: UNITED AIRLINES

```

Find the system.time() for the original size data, 20x the data, and 40x the data
```{r}
# we have to create copies
CopyAirlineStrikes <- AirlineStrikes

TwoAirlineStrikes <- rbind(AirlineStrikes, CopyAirlineStrikes)

FourAirlineStrikes <- rbind(TwoAirlineStrikes, TwoAirlineStrikes)

EightAirlineStrikes <- rbind(FourAirlineStrikes, FourAirlineStrikes)

SixteenAirlineStrikes <- rbind(EightAirlineStrikes, EightAirlineStrikes)

TwentyAirlineStrikes <- rbind(SixteenAirlineStrikes, FourAirlineStrikes)

FortyAirlineStrikes <- rbind(TwentyAirlineStrikes, TwentyAirlineStrikes)


# Find times for the data
Start1 <- Sys.time()
mostStrikes(AirlineStrikes)
End1 <- Sys.time()

Start20 <- Sys.time()
mostStrikes(TwentyAirlineStrikes)
End20 <- Sys.time()

Start40 <- Sys.time()
mostStrikes(FortyAirlineStrikes)
End40 <- Sys.time()


# Calculate runtime
Runtime1 <- End1 - Start1
Runtime20 <- End20 - Start20
RUntime40 <- End40 - Start40


# Get the number of elements in each dataset using nrow()
Observations1 <- nrow(AirlineStrikes)
Observations20 <- nrow(TwentyAirlineStrikes)
Observations40 <- nrow(FortyAirlineStrikes)


# Create a dataframe with the data calculated
TestDF <- data.frame(Observations = c(Observations1, Observations20, Observations40),
                   Time = c(Runtime1, Runtime20, RUntime40))

# With the data created, plot it
plot(TestDF$Observations, TestDF$Time, type = "o",
     xlab = "Elements", ylab = "Time", main = "mostStrikes Complexity")

```

As can be seen by the chart, the function can be described as O(n) runtime,
as when the number of elements increases, the runtime increases linearly as well.


