---
title: "VALLURU_M_7"
output: html_notebook
---


Set the working directory
```{r}
setwd("D:/Mahitha/DataScience/HW7/")
```


Convert the downloaded csv file into a dataframe
```{r}
loadDF <- function() {
  if(!exists("demographics")) {
    demographics <- read.csv("Data Science - Demographics of India - Sheet1.csv", header = TRUE)
  }
}
```


To show that this is in fact a dataframe, we can call its class type:
```{r}
class(demographics)
```


To show that this is a dataframe, I can also print it out and show it to you:
```{r}
print(demographics)
```

As you can see, this data looks very clean, and the only thing I would personally do to clean this data is to remove the "Rank" row which is at the far left. Although it may have some symbolic meaning - the order of states by population from greatest to least - it is not necessary to have a separate row to show that. It can quite simply be written as a remark and also can be very easily seen by someone analyzing this data.