---
title: "VALLURU_M_9"
output: html_notebook
---

Load libraries

```{r}
install.packages("RMySQL")
library(RMySQL)
library(DBI)
```


Set working directory.
```{r}
setwd("D:/Mahitha/DataScience/HW9/")
```


Function that loads the csv file
```{r}
loadDF <- function() {
  if(!exists("birdstrikes")) {
    temp <- read.csv("birdstrikes.csv")
  }
}
```


Only keep certain columns for birdstrikes
```{r}
birdstrikes <- temp[,c(1,2, 6, 10, 11, 15, 16, 34)]
```


Clean up the date column format.
There is a format called POSIX, and I'll be using that.
```{r}
birdstrikes$FlightDate <- as.POSIXct(birdstrikes$FlightDate, format="%m/%d/%Y")
```



Now, I'll be creating tables to organize my data.
There will be sevearl tables:
  1. Aircraft Type
  2. Origin
  3. Airline Operator
  4. Impact to Flight
  5. Incident


This will be the creation of the Aircraft type table
```{r}
type_id <- 1:length(levels(birdstrikes$Aircraft..Type))
type <- levels(birdstrikes$Aircraft..Type)  # The type of Aircraft, so "", Airplane, C, or Helicopter
aircraft <- data.frame(type_id, type)

aircraft$type[aircraft$type == ""] <- NA   # let all incomplete data be equal to NA
```



This is the Airports table
```{r}
origins <- birdstrikes[, c("Airport..Name", "Origin.State")]

origins$Airport..Name[origins$Airport..Name == "UNKNOWN"] <- NA  # let all data with unknown values be set to NA
origins$Airport..Name[origins$Airport..Name == ""] <- NA         # let all incomplete data be equal to NA

origins <- unique(origins)   # get rid of all duplicate data, we only want the unique ones

origins$origin_id <- 1:nrow(origins)  # add an ID, of course
```



This is the Airline Operators table
```{r}
op_id <- 1:length(levels(birdstrikes$Aircraft..Airline.Operator))
op_name <- levels(birdstrikes$Aircraft..Airline.Operator)   # includes all the operators for airplanes

operators <- data.frame(op_id, op_name)

```


This is the Impact to Flight table
```{r}
effect_code <- 1:length(levels(birdstrikes$Effect..Impact.to.flight))
description <- levels(birdstrikes$Effect..Impact.to.flight)   # includes the description of what happened to the flight, if anything

effects <- data.frame(effect_code, description)

effects$description[effects$description == ""] <- NA  # clean the descriptions, anything empty will be NA
```




This is the Incidents table
```{r}

incidents <- birdstrikes

incidents$Aircraft..Type <- aircraft$type_id[match(incidents$Aircraft..Type, aircraft$type)]

incidents$Effect..Impact.to.flight <- effects$effect_code[match(incidents$Effect..Impact.to.flight, effects$description)]

incidents$Aircraft..Airline.Operator <- operators$op_id[match(incidents$Aircraft..Airline.Operator, operators$op_name)]


# Because a lot of the tables have an ID as a column, here is a function that gets the ID.
getId <- function(x,y) {
  
  if (is.na(x)) {
    id <- origins$origin_id[which(is.na(origins$Airport..Name) & origins$Origin.State == y)]
  } 
  
  else {
    id <- origins$origin_id[which(origins$Airport..Name == x & origins$Origin.State == y)]
  }

  id <- as.numeric(id)

  return(id)

}

# Now for some cleaning
incidents$Airport..Name[incidents$Airport..Name=="UNKNOWN"] <- NA
incidents$Airport..Name[incidents$Airport..Name==""] <- NA
incidents$origin <- mapply(getId, incidents$Airport..Name, incidents$Origin.State)
incidents <- incidents[-c(2,7)]
incidents$Feet.above.ground[incidents$Feet.above.ground==""] <- NA



```





```{r}
write.table(aircraft,"aircraft.csv", col.names=TRUE, row.names=FALSE, na="NULL", quote=TRUE)

write.table(effects, "effects.csv",  col.names=TRUE, row.names=FALSE, na="NULL", quote=TRUE)

write.table(operators, "operators.csv",  col.names=TRUE, row.names=FALSE, na="NULL", quote=TRUE)

write.table(origins, "origins.csv",  col.names=TRUE, row.names=FALSE, na="NULL", quote=TRUE)

write.table(incidents, "incidents.csv",  col.names=TRUE, row.names=FALSE, na="NULL", quote=TRUE)
```



Connect to MySQL
```{r}
mydb <- dbConnect(MySQL(), 
                  user="XXX", 
                  host="localhost",
                  password="XXX", 
                  dbname="birdstrikes")
```


```{r}
con <- dbConnect(MySQL(),
                 user = "root",
                 password = "XXX",
                 host = "127.0.0.1",
                 port = 3306,
                 dbname = "birdstrikes")

dbWriteTable(conn = con, name = "Aircraft", value = as.data.frame(aircraft))

dbWriteTable(conn = con, name = "Effects", value = as.data.frame(effects))

dbWriteTable(conn = con, name = "Incidents", value = as.data.frame(incidents))

dbWriteTable(conn = con, name = "Operators", value = as.data.frame(operators))

dbWriteTable(conn = con, name = "Origins", value = as.data.frame(origins))

```


```{r}
# What is the total number of birdstrikes
dbGetQuery(mydb, "SELECT count(*) FROM incidents")

# Number of birstrikes by airline
dbGetQuery(mydb, "SELECT airline_name, count(*) FROM operators, incidents WHERE incidents.operator = operators.op_id GROUP BY airline_name")

# Number of birdstrikes with Origin from Boston
dbGetQuery(mydb, "SELECT count(*) FROM incidents i, origins o WHERE i.origin = o.origin_id AND o.airport_name = \"LOGAN INTL\"")

# birdstrike incidents above 10,000 feet
dbGetQuery(mydb, "SELECT count(*) FROM incidents WHERE height > 10000")

# birdstrike incidents each month for a given year
dbGetQuery(mydb, "SELECT count(*) FROM incidents i WHERE i.year = x")

```












