---
title: "VALLURU_M_5"
output: html_notebook
---

Load any required libraries.
```{r}
library(XML)
```


Function that loads the data.
Args: None
Returns: None
```{r}
loadDF <- function() {
  if (!exists("senators")) {
    senators <- xmlToDataFrame("http://ds4100.weebly.com/uploads/8/6/5/9/8659576/senators.xml")
  }
}
```

Loads the data frame.
```{r}
loadDF()
```



Returns all of the names of senators from the given state.
Args: STATE - the abbreviation of one of the 50 US states.
Returns: A vector of all of the senators that are form the given state.
```{r}
senatorsFrom <- function(STATE) {
  
  # creates a new dataframe with all of the senators from the given state
  byState <- senators[senators$state == STATE,]
  
  # for loop that adds the first and last names of the senators to a vector
  for(i in 1:nrow(byState)) {
    namesByState <- paste(byState$first_name, byState$last_name) # I did it by first name then last name
  }
  
  # return the vector
  return(namesByState)
}
```




Returns the phone number of the given senator.
Args: NAME - an argument that represents the name of the senator. The format is "lastname, firstname" in a string.
Returns: A phone number of the given senator.
```{r}
senatorPhone <- function(NAME) {
  
  # Create a dataframe with 3 columns:
  # - last_name
  # - first_name
  # - phone
  cleanNames <- senators[, c(2,3,7)]
  
  # Create a new column in the cleanNames dataframe
  cleanNames$combine <- " "
  
  # With this new column, fill it with the last and first names combined
  for(i in 1:nrow(cleanNames)) {
    name <- paste(cleanNames[i,1], cleanNames[i,2], sep = ", ") # combine last and first, separated by a comma
    cleanNames[i,4] <- name # add this name to the appropriate row of the column
  }
  
  # new for loop for comparing if the given name equals any of the names in the dataframe
  # I made a new for loop instead of just using the for loop above because this loop is for a different purpose,
  # so I thought thi was effective.
  for(i in 1:nrow(cleanNames)) {
    # converts the name in the row of the combine column into a string to compare
    stringConvert <- toString(cleanNames[i,4])
    # compares the given to the element in the dataframe
    if(stringConvert == NAME) { 
      return(cleanNames[i,3])
      }
  }
  
  
}
```





Creates a dataframe with all of the senators' last names sorted and phone numbers.
Args: None
Returns: None.
```{r}
listSenators <- function() {
  # create a new dataframe
  lastPhone <- senators[, c(2, 7)] # keep in mind that the last names are already sorted, so there is no need to sort
  
}
```


